---
title: "Applied process"
author: "Amin Bazaz, Heraldo Borges, Eduardo Ogasawara"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example with a sample dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This documentation is intended to present the outputs of a sample dataset.

```{r, echo=FALSE}
source(file = "../R/mainFunction.R")
source(file = "../R/subFunction.R")
source(file = "../R/visualization.R")
library(foreach)
library(stats)
library(ggplot2)
library(reshape2)
```

### Launch the workflow to find the motifs

The workflow consists of 3 steps described in the main package documentation.
These 3 steps will be applied on our sample.

 1. The function `STSIdentifyCandidateSTMotifs` allows to generate the candidates:

```{r, echo=TRUE}

# The process is launched on the provided example dataset
dim(STMotif::example_dataset)


# Generation of candidates
candidates <- STSIdentifyCandidateSTMotifs(data = STMotif::example_dataset, tslice = 25, sslice = 10, alpha = 7, window_size = 3)


# Information of the block 1
# The candidates built 
head(candidates$motifs[[1]]$Subs)[1:3,]

# The candidates built with SAX
head(candidates$motifs[[1]]$Subs.SAX)[1:3,]

# Grouping identical candidates 
head(candidates$motifs[[1]]$Motif.raw)[1:3]

# Grouping identical motifs with SAX
head(candidates$motifs[[1]]$Motif.SAX)[1:3]

# Grouping the starting position of identical candidates in the combined series
head(candidates$motifs[[1]]$Indices)[1:3]


# Number of blocks in horizontal and vertical
c(candidates$nrows,candidates$ncols)


# Position of the block 1 into the original dataset
candidates$rectangles[[1]]

# Values of block 1
head(candidates$blocks$datasets[[1]])[1:3,]


# Encoded values of block 1
head(candidates$saxblocks$datasets[[1]])[1:3,]
```
 

 2. The functions `STSIdentifySTMotifs` and `STSIdentifyTightSTMotifs` allows to check and filter the candidates:
 
```{r, echo=TRUE}
stmotifs <- STSIdentifySTMotifs(candidates = candidates, ka = 1, si = 1)

# Output of the first selected motif
stmotifs[[1]]
``` 
```{r, echo=TRUE}
sttightmotifs <- STSIdentifyTightSTMotifs(stmotifs = stmotifs, rectangles = candidates$rectangles)

# Output of the first motif after removing the isolated
sttightmotifs[[1]]
``` 
 
 3. The function `STSRankTightSTMotifs` allows to rank the selected motifs by their quality:
 
```{r, echo=TRUE}
ranksttightmotifs <- STSRankTightSTMotifs(sttightmotifs = sttightmotifs)

# Motif with the better quality
ranksttightmotifs[[1]]
```


### Plot the result

The function `runVisualization` allows to launch the shiny application to see the result.
There are two ways to visualize the result.

- Plot the intensity of values and highlight one or the top five motifs.

```{r fig, fig.height = 4, fig.width = 6, fig.align = "center"}
# Plot the intensity of the dataset and highlight one selected motif
intensityDataset(dataset = STMotif::example_dataset,rankList = ranksttightmotifs,position = 1,alpha = 7)
```

- Plot the spatial-time series by selecting a range of columns in the dataset and highlight one motif

```{r fig1, fig.height = 4, fig.width = 6, fig.align = "center"}
# Plot five specific spatial-series which some of them contain the best motif
displayPlotSeries(dataset = STMotif::example_dataset, rankList = ranksttightmotifs ,position = 1 ,space = c(1,2,5:7))
```
